ML Estimation of Matrix t Distributions with Expectation Maximization

### 2017-01-05 paper.tex
Working on introduction paragraph.

\begin{abstract}
We provide expectation-maximization (EM) formulae for the maximum
likelihood estimation of matrix--$t$ distributions and discuss their
practical implementation.  The result can be applied to problems where
the parameters of a matrix--$t$ distribution need to be obtained from
data, such as the design of recommendation systems, or remote sensing
algorithms.
\end{abstract}

\paragraph{Introduction}
Matrix--$t$ distributions have been applied to several predictive
problems, such as spatial interpolation applied to the prediction of
pollution concentration \citep{KIBRIA2006785}, recommendation systems
\citep{NIPS2007_3203}. In these situations it is necessary to obtain
the parameters of the metrix--$t$ distribution (consisting of the
number of degrees of freedom, a location matrix and two scale
matrices) that describe a set of given matrix valued observations.
While the exact formulae for Maximum Likelihood Estimation (MLE) are
unwieldy and slow to compute, the problem can be simplified if instead
we obtain the distribution parameters using Expectation-Maximization
(EM). We obtain can obtain the EM expressions by viewing the
matrix--$t$  distribution as a matrix-normal distribution where one of
the scale matrices is sampled from a Wishart distribution.

>>>>

\begin{abstract}
We provide expectation-maximization (EM) formulae for the maximum likelihood estimation of matrix--$t$ distributions and discuss their practical implementation. The result can be applied to problems where the parameters of a matrix--$t$ distribution need to be obtained from data, such as the design of recommendation systems and remote sensing algorithms.
\end{abstract}

\paragraph{Introduction}
Matrix--$t$ distribution is a generalization of multivariate $t$ distribution to matrix variates situations. Similar as other $t$ distributions, matrix--$t$ distribution is a scale mixture of a particular class of multivariate normal models, matrix normal distributions \citep{}, except the mixture parameter is a matrix rather than a scalar. Due to this, the distribution shares the importance in robust estimation and has been applied to many predictive tasks such as spatial interpolation on the prediction of pollution concentration \citep{KIBRIA2006785}, recommendation systems \citep{NIPS2007_3203}, and ... In these problems, it is necessary to obtain the parameters of the distribution, which consist of a degrees of freedom parameter, a matrix location parameter, and two scale matrix parameters, that describe a set of given matrix--valued observations for further inference.

A common approach on estimating the parameters is through the method of maximum likelihood (ML). However, optimizing the likelihood directly is a formidable task and the gradient equations are unwieldy and slow to compute and solve. For $t$-distributions, it is well-known that one can exploit the scale mixture property and ...... he problem can be simplified if instead
we obtain the distribution parameters using Expectation-Maximization
(EM). We obtain can obtain the EM expressions by viewing the
matrix--$t$  distribution as a matrix-normal distribution where one of
the scale matrices is sampled from a Wishart distribution.
